WSClean: an implementation of a fast, generic wide-field imager

### 2014-02-05 articles/2014/Article-WSClean/wsclean.tex
Some work on article

It is possible to combine the $w$-projection and $w$-stacking algorithms by gridding on several $w$-layers to which the large $w$-terms are corrected after the FFT, and using a $w$-correcting kernel for making small $w$-corrections, thereby projecting them on the nearest $w$-layer. This allows using small $w$-kernels and limits at the same time the number of FFTs and required memory. The AWImager has been applied like this, which let to better results compared to $w$-projection without $w$-stacking \citep{awimager-2013}. For this scenario, Eq.~\eqref{eq:casa-computing-cost} can be used to determine the optimal number of $w$-layers, or more general the optimal distance between layers, by assuming that the cost of calculating a single $w$-layer equals the cost of imaging the data set with correspondingly smaller $w_e$ value and smaller $N_\textrm{vis}$. If $\Delta w$ is the distance between $w$-layers, then 
\begin{equation}
t(\Delta w) = \frac{w_e}{\Delta w} t_\textrm{CASA}(w'_e,N'_\textrm{vis},N_\textrm{freq},N_\textrm{pix}),
\end{equation}
with $N'_\textrm{vis} = \frac{N_\textrm{vis}\Delta w}{w_e}$ and $w'_e = \Delta w$.

>>>>

It is possible to combine the $w$-projection and $w$-stacking algorithms by gridding onto several $w$-layers to which large $w$-terms are corrected after the FFT, and using a $w$-correcting kernel for making small $w$-corrections. This allows using small $w$-kernels and limits at the same time the number of FFTs and required memory. The AWImager has been applied like this, which let to better results compared to $w$-projection without $w$-stacking \citep{awimager-2013}. For this scenario, Eq.~\eqref{eq:casa-computing-cost} can be used to determine the optimal number of $w$-layers, or more general the optimal distance between layers, by assuming that the cost of calculating a single $w$-layer equals the cost of imaging the data set with correspondingly smaller $w_e$ value and smaller $N_\textrm{vis}$. If $\Delta w$ is the distance between $w$-layers, then 
\begin{equation}
t(\Delta w) = \frac{w_e}{\Delta w} t_\textrm{CASA}(w'_e,N'_\textrm{vis},N_\textrm{freq},N_\textrm{pix}),
\end{equation}
with $N'_\textrm{vis} = \frac{N_\textrm{vis}\Delta w}{w_e}$ and $w'_e = \Delta w$.
